RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-12-19 paper.tex
yes
working
notes
abstract note

@@

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Individual data scientists and statisticians usually
  work on loosely related problems, and must devise effective ways to
  share their findings and move results from exploratory data analysis
  into automated diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, EDA environments often assume a single-developer perspective,
  while data scientist teams would get much benefit from easier sharing
  of scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide. We contribute and justify the following three
  requirements for systems built to support current data science teams
  and users: \emph{technology transfer}, \emph{coexistence}, and
  \emph{discoverability}. In addition, we contribute the design and
  implementation of RCloud, a prototype system that supports the requirements
  collaborative data analysis, visualization and web deployment. We
  discuss the design decisions, tradeoffs and limitations, and compare RCloud
  to other current proposals.
} % end of abstract

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{Some, Keywords, Here}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.3\linewidth]{fig/screenshots/wdcplotsmall.jpg}
  %% \includegraphics[width=.9\linewidth]{figs/teaser.jpg}
  % \vspace{-.5em}
  \caption{RCloud provides infrastructure for data science teams so
    that R \emph{hackers} and \emph{scripters}~\cite{Kandel:2012:EDA} can target modern
    interactive visualization technologies such as
    D3~\cite{Bostock:2011:DDD}, dc.js~\cite{DCJS:2014:DC} and
    Crossfilter~\cite{Square:2014:CFM} (left), while at the same time
    enabling seamless deployment and dashboarding for
    \emph{application users} (right)
  }
% \vspace{-.5em}
}

>>>>

%\usepackage{dblfloatfix}
%\usepackage{fixltx2e}
\usepackage{url}

@@

%% Abstract section.
\abstract{ Consider the emerging role of a data science team within an
  organization. Individual data scientists and statisticians usually
  work on loosely related problems, and must devise effective ways to
  share their findings and move results from exploratory data analysis
  into automated diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, EDA environments often assume a single-developer perspective,
  while data scientist teams would get much benefit from easier sharing
  of scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide. We contribute and justify the following three
  requirements for systems built to support current data science teams
  and users: \emph{technology transfer}, \emph{coexistence}, and
  \emph{discoverability}. In addition, we contribute the design and
  implementation of RCloud, a system that supports the requirements
  collaborative data analysis, visualization and web deployment. We
  discuss the design decisions, tradeoffs and limitations, and compare RCloud
  to other current proposals.
  \carlos{RCloud has been in production use for more than a year and has about one hundred active users. We will discuss the adoption issues and etc etc.}
} % end of abstract

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{visual analytics process, provenance, collaboration, visualization, computer-supported cooperative work}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.28\linewidth]{fig/screenshots/wdcplotsmall.jpg}
  %% \includegraphics[width=.9\linewidth]{figs/teaser.jpg}
  \hspace{1em}
  \includegraphics[width=.6\linewidth]{fig/casestudy1/casestudy1.graffle/image8.png}
  % \vspace{-.5em}
  \caption{RCloud provides infrastructure for data science teams so
    that R \emph{hackers} and \emph{scripters}~\cite{Kandel:2012:EDA} can target modern
    interactive visualization technologies such as
    D3~\cite{Bostock:2011:DDD}, dc.js~\cite{DCJS:2014:DC} and
    Crossfilter~\cite{Square:2014:CFM} (left), while at the same time
    enabling seamless deployment and dashboarding for
    \emph{application users} (right).
    \carlos{Replace this with something using either a Shiny demo or in-process nanocubes?}
  }
% \vspace{-.5em}
}
